### 2010-04-07 docs/architecture/architecture.tex
started writing up fancy bottom solver - will finish when I get a chance

\section{Multigrid}

>>>>

\section{Multigrid}
\subsection{\tt bottom\_solver\_type = 4}
We have a special bottom solver type that greatly speeds up large problems.
In fact, you should use this bottom solver whenever possible, because in 
testing, it always speeds up the multigrid, even if the problem is relatively 
small.  What this solver essentially does is take the grid structure and
data from the coarsest level of multigrid, and copy it onto a new grid
structure with fewer, larger grids, with the intent of further coarsening
this ``new'' problem so the ``new'' bottom solver has fewer data points on
a smaller number of grids.  If you want to enable this solver for the nodal 
solver, set {\tt hg\_bottom\_solver = 4} in your inputs file.  If you want 
to enable this solver for the cell-centered solver, set 
{\tt mg\_bottom\_solver = 4} in your inputs file.

To understand how this bottom solver work, the first thing you need to know
is what the grid structure of the coarsest level of your multigrid V-cycle
looks like.  Now, figure out what the size of a single box would be if you
wanted it to fit all the data at the bottom level.  Now, figure out what
the largest integer $n$ is so that you can evenly divide this single box
by $2^n$ in every coordinate direction.  If $n < 2$, the program will abort
since the grid structure is not suitable for this bottom solver.

{\tt max\_mg\_bottom\_nlevs}
